INTELLIGENT SYSTEMS

### 2021-04-05 slides.tex
Slide paper4 Evaluations

\documentclass[10pt]{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{biblatex}
\usepackage{adjustbox}
\usepackage[font=scriptsize]{caption}
\usepackage{subcaption}
\captionsetup[figure]{labelsep=period}
\captionsetup[subfigure]{labelformat=simple} % default is 'parens'
\renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

@@

>>>>

\documentclass[10pt]{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{biblatex}
\usepackage{adjustbox}
\usepackage[font=scriptsize]{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\captionsetup[figure]{labelsep=period}
\captionsetup[subfigure]{labelformat=simple} % default is 'parens'
\renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

@@

\section{Paper 4}
\subsection{\emph{"A Data Set for Camera-Independent Color Constancy"}}

\begin{frame}{INTRODUCTION}
    In computer vision, the output generated by an algorithm depends on the 
    nature of the images set given as input. When the images come from 
    different sources (e.g. different cameras), the behavior of the algorithm is 
    not always the same. For this reason, we try to standardize the input in 
    order to have a more uniform output.
\end{frame}

\begin{frame}{COLOR CONSTANCY DATASETS}
    To produce uniform output, an algorithm must achieve "{\bfseries{color 
    constancy}}" on all input images. In order to calculate this property, there 
    are supervised and unsupervised algorithms. To test the performance of 
    these algorithms, there are already state-of-the-art datasets \footfullcite{0807099130} \footfullcite{0807099132} \footfullcite{0807099120}
    containing indoor and outdoor images, but these have few images inside 
    them.
\end{frame}

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET}
    The purpose of the paper is to present a dataset containing images useful 
    for researching the {\bfseries{camera/scene-independence}} effect of an algorithm.
    To achive this, each scene was captured under five different illumination. 
    In each scene there are images taken from three different cameras, 
    including a mobile one.
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/lab.png}
        \centering
        \caption{Lab real scenes}
        \label{fig:Lab}
    \end{figure}
\end{frame}

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Chromaticity}
    \begin{block}{Chromatic adaptation - \href{https://en.wikipedia.org/wiki/Color_vision}{\underline{Wikipedia}}}
        \emph{"In color vision, chromatic adaptation refers to color constancy; the 
        ability of the visual system to preserve the appearance of an object under 
        a wide range of light sources."}
    \end{block}
    The only information available on the light source are: the "\emph{Spectral 
    Power Distributions}" (SPD) and the "\emph{Spectral Reflectance}" (SR)
    Thanks to this information, we can obtain the existing chromaticity in the image 
    and compare it with that obtained from the "\emph{Camera Spectral Senstivities}" (CSS).
    \begin{block}{Target}
        The goal is to be able to bring the white point, calculated by each algorithm, closer to the white point of the ground truth, within the same color spectrum (sRGB). To do this, a "\emph{Color Conversion Matrix}" (CMM) is used.
    \end{block}
\end{frame}

\begin{frame}{THE PROPOSED INTEL-TUT DATA SET - Evaluations}
